Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-13 presentations/bsa_2020-07-27/index.Rmd
Update slides

---
## Bioregions

Most sites fall into four bioregions

```{r tax-bioregion, out.width = "120%", fig.asp = 0.7}
ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light()
```

>>>>

---
## Most sites fall into four bioregions

```{r tax-bioregion, out.width = "120%", fig.asp = 0.7}
ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_light() +
  labs(
    title = "Taxonomic bioregions"
  )
```

---
## Taxonomic and phylogenetic bioregions are similar

```{r tax-bioregion, out.width = "120%", fig.asp = 0.7}
a <- ggplot(ses_div_ferns_spatial, aes(fill = taxonomic_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_carto_d(name = "Cluster", type = "qualitative", palette = "Bold") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme_pp_light() +
  labs(
    title = "Taxonomic bioregions"
  ) +
  theme(legend.position = "none")

# Swap first two colors to get them to match between taxonomic and phylogenetic plots
cols_old <- rcartocolor::carto_pal(n = 8,  "Bold")
cols <- cols_old
cols[1] <- cols_old[2]
cols[2] <- cols_old[1]

b <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_manual(values = cols) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(title = "Phylogenetic bioregions") +
  map_theme_pp_light() +
  theme(
    axis.text.y = element_blank(),
    legend.position = "none")

a + b 
```

---
## Bioregions mostly match traditionally-defined forest types

```{r tax-bioregion, out.width = "120%", fig.asp = 0.7}
forest_types <- image_read(here::here("presentations/bsa_2020-07-27/images/forest_types_3_eng.png"))

b <- cowplot::ggdraw() + 
  cowplot::draw_image(forest_types)

a <- ggplot(ses_div_ferns_spatial, aes(fill = phylo_cluster)) +
  geom_sf(color = "transparent") +
  scale_fill_manual(values = cols) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  labs(title = "Phylogenetic bioregions") +
  map_theme_pp_light() +
  theme(
    axis.text.y = element_blank(),
    legend.position = "none")

a + b 
```
